Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-17 paper/paper.tex
minor

Operational semantics of Anglican queries is different from that
of Clojure code, therefore queries must be called through
inference algorithms, rather than `directly'. \iftoggle{full}{The
\texttt{anglican.inference} namespace}{Anglican} declares the (ad-hoc) polymorphic
function \texttt{infer} using Clojure's multimethod mechanism.
This function accepts an Anglican query and
returns a lazy sequence of weighted samples from the
distribution defined by the query.  When inference
is performed on an Anglican query, the query is run by a
particular inference algorithm. Inference algorithms must
provide an implementation for \texttt{infer}, as well as
override the polymorphic function \texttt{checkpoint} (defined
as a multimethod) so as to handle \texttt{sample} and
\texttt{observe} in an algorithm-specific manner and
to construct an appropriate result on the
termination of a probabilistic program.

>>>>

%Operational semantics of Anglican queries is different from that
%of Clojure code, therefore queries must be called through
%inference algorithms, rather than `directly'. 
Operational semantics of an Anglican query is different from that
of Clojure code, and is determined by an inference algorithm. Thus,
Anglican queries must be called through these inference algorithms, rather
rather than `directly'. For this purpose,
\iftoggle{full}{the
\texttt{anglican.inference} namespace}{Anglican} declares the (ad-hoc) polymorphic
function \texttt{infer} using Clojure's multimethod mechanism.
The function accepts and runs an Anglican query, 
and returns a lazy sequence of weighted samples from the
distribution defined by the query. Providing an implementation of this function
is a responsibilit of an inference algorithm, which should also
override the polymorphic function \texttt{checkpoint} (defined
as a multimethod) so as to handle \texttt{sample} and
\texttt{observe} in an algorithm-specific manner and
to construct an appropriate result on the
termination of a probabilistic program.

%When inference
%is performed on an Anglican query, the query is run by a
%particular inference algorithm. Inference algorithms must
%provide an implementation for \texttt{infer}, as well as
%override the polymorphic function \texttt{checkpoint} (defined
%as a multimethod) so as to handle \texttt{sample} and
%\texttt{observe} in an algorithm-specific manner and
%to construct an appropriate result on the
%termination of a probabilistic program.
